{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-09-10 documents/supplemental.tex
Quick ol' FDTD sim of lung
Wonderful turbidimeter

\documentclass[paper.tex]{subfiles}
\begin{document}

@@

>>>>

%!TeX root = supplemental
\documentclass[paper.tex]{subfiles}
\begin{document}

@@

\PRLsep{{\itshape Turbidimeter }}

Essentially the only method of determining the activity of phage is to have it infect a suitable host.

Typically, this is done either in a large tube or a flat-sided optical cuvette.

Because the variation in the optical density is quite small, this poses some rather.

A small vial of liquid has a much larger surface area relative to its thermal mass. sis removed, the temperature drops very rapidly; if the temperature drops outside the physiological range of about 33-40 C, growth is stunted.\cite{effect2003}

As a faculative aerobe, E.coli requires a concentration of oxygen to be present in the mixture for speedy replication \cite{Effect1965}; and this supply must also be kept sterile. One method to ensure this is by using a bubbler aerator; Carolina recommends an aquarium pump with cotton-ball filters.

Another method, often used in microfluidics\cite{Microfluidic}, is that of \cite{method1951}; manganese dioxide catalyzed decomposition of hydrogen peroxide. MnO2 is readily obtained from alkaline batteries; and in this case no sterility issues are presented. However, it is not obvious how all h2o2 vapor can be prevented from contacting the culture.

Bottles of zero air may be more effective.

In commercial fluid transfer machines, this is often resolved by HEPA filtering the input to the cabinet.

Shaking incubators, which simply rock the

In our case, ensuring that a great deal of headspace was present in the tube was sufficient for brief growth.

As the size of the well decreases, the Reynolds number also decreases \footnote{In fact, in the case of a circular well, it's not obvious that this is the case - the cross section decreases faster than the characteristic length}, and turbulent flow is greatly hampered.

Using 2.5 mm diameter x 3 mm high wells cut in polycarbonate and sealed with clear packing tape. However, the presence of small bubbles in the headspace of the wells prevented a consistent reading.

We tried simply adding 1 uL of culture to the microscope slide;

The 8-bit resolution of most cameras did not seem sufficient to discern the turbidity.

\cite{Vision2016} use an ingenious technique.
